How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-11 20220210_Draft.Rmd
Updated rmarkdown to take a look at the non matched codes (other category)

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar| |internacionalizacao")

@@

# Visualize totals
tibble::tibble(Sovereignty = sum(AS_long$sovereignty),
               Development = sum(AS_long$development),
               Conservation = sum(AS_long$conservation),
               Other = sum(AS_long$other))
# Still some overlap... 
```

>>>>

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|soberana|soberano|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|exercito|dono|internacionalizar|internacionalizacao")

@@

# Visualize totals
tibble::tibble(Sovereignty = sum(AS_long$sovereignty),
               Development = sum(AS_long$development),
               Conservation = sum(AS_long$conservation),
               Other = sum(AS_long$other))
# Still some overlap...Also, there were 976 context units not matched at all...
# Let's see some of which is not matched
o <- dplyr::filter(AS_long, other == 1) %>% dplyr::select(president, year, context)
dplyr::slice_sample(o, n = 20)
o$context[1:20] # Number 12 and 17 (riquezas no subsolo/mineral reserves) development?
o$context[500:520] # Number 7, development or preservation or neither? 10 (chico mendes) preservation? 14 sovereingty? 15 development and sovereingty? 17 and 18 development? 19 and 20 conservation? 21 development?
o$context[940:960] # 1 (gas and niobio) development? 3 sovereignty? 6 development and preservation? 7 conservation? A lot of Bolsonaro's mentions about the Amazonia not burning, should we code these or not? 
```
